\documentclass{bioinfo}
\copyrightyear{2020} \pubyear{2020}

\access{Advance Access Publication Date: Day Month Year}
\appnotes{Manuscript Category}

\begin{document}
\firstpage{1}

\subtitle{Structural Bioinformatics}

\title[MolSysMT]{MolSysMT: A computational laboratory bench to work with biomolecular systems in Python.}
\author[D. Prada-Gracia \& L.M. Moreno-Vargas]{Diego Prada-Gracia$^{\text{\sfb 1,}*}$ and Liliana M. Moreno-Vargas$^{\text{\sfb 1,}*}$}
\address{$^{\text{\sf 1}}$Computational Biology and Drug Design Research Unit, Mexico City
Children's Hospital Federico Gómez, Mexico City, 06720, Mexico.}

\corresp{$^\ast$To whom correspondence should be addressed.}

\history{Received on XXXXX; revised on XXXXX; accepted on XXXXX}

\editor{Associate Editor: XXXXXXX}

\abstract{\textbf{Summary:} Bla, bla, bla.\\
\textbf{Availability and implementation:} The open source code is available at the
\href{https://github.com/uibcdf/MolSysMT}{uibcdf/MolSysMT GitHub repository} to be used, modified
and shared according to the MIT License. A conda package with the latest stable version is distributed through the
\href{https://anaconda.org/uibcdf/molsysmt}{"uibcdf" conda channel}. And installation
instructions, user's documentation and jupyter notebooks with illustrative examples are available
at \href{http://www.uibcdf.org/MolSysMT}{http://www.uibcdf.org/MolSysMT}.\\
\textbf{Contact:} \href{prada.gracia@gmail.com}{prada.gracia@gmail.com},
\href{lm.moreno.vargas@gmail.com}{lm.moreno.vargas@gmail.com}
}

\maketitle

\section{Introduction}

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Text Text Text  Text Text \citep{Bag01}.

\section{The computational work with biomolecular models.}

Explain the concept of lab bench.
Implementing workflows.

\section{Implementation}

Text Text Text Text Text Text Text Text
Text Text Text Text Text Text Text Text Text Text Text Text Text.

\subsection{Subsection 1}

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.

\subsubsection{Subsubsection 11}

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.

\subsection{Subsection 2}

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.

\section{Conclusion}

Text Text Text Text Text Text  Text Text Text
Text Text Text Text Text Text  Text Text Text Text Text Text.

\section*{Funding}

This work has been partially supported by the Fondos Federales project SSA XXX at Institutos de
Salud.\vspace*{-12pt}

%\bibliographystyle{natbib}
%\bibliographystyle{achemnat}
%\bibliographystyle{plainnat}
%\bibliographystyle{abbrv}
%\bibliographystyle{bioinformatics}
%
%\bibliographystyle{plain}
%
%\bibliography{Document}

\begin{thebibliography}{}

\bibitem[Bag {\it et~al}., 2001]{Bag01}
Bag,M., Name2, Name3 (2001) Article title, {\it Journal Name}, {\bf 99}, 33-54.

\end{thebibliography}
\end{document}
